---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# esemchart

<!-- badges: start -->
<!-- badges: end -->

A common task for psychological students is the organization of statistical output.It can be tough when organizing useful data from lots of output especially adapting a scale.The goal of esemchart is to generate tables for parameters and loadings made by lavaan::cfa function or esemComp package.Using this package may
minimize transcription errors and reduce the time researchers use.

## Installation

You can install the development version of esemchart like so:

``` r
# install.packages(esemchart)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(esemchart)
library(flextable)
## use a data to run a normal CFA model
data2<-lavaan::HolzingerSwineford1939
data2<-data2[,c(7:15)]
model1<-'visual=~x1+x2+x3'
fit<-lavaan::cfa(model1,data2)

# You can transform the output of cfa function to basic table matters 
table<-apa.loading.table(fit,table.number=1,model="cfa")

# Then you can make an APA table for the CFA
la<-c("f1")
item<-list("amo1","amo2","amo3")
create_tab(table,la,item,title="CFA loading",model="cfa")

#If you have lots of items loading on different factors,then you can use the itemname function to generate a name list.
namelist<-list(f1=c(1:4),f2=c(5:8))
itemname(namelist,data2)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
